---
title: "DATA 308: Homework 3"
subtitle: "Simple linear regression"
author: "Dylan Wikel"
format: 
  html:
    echo: true
    message: false
    warning: false
    toc: true
    toc-depth: 4
    embed-resources: true
---

*Please change the author name to your own. Answer in complete sentences.*

# Bike share data

We have data on bike ridership among registered members of the Capital Bikeshare service in Washington, D.C. rentals by weather.

## Question 0

Begin by running the code chunk below to load the `tidyverse` package and the `bikes` data from the `bayesrules` package. You may need to first install the packages using `install.packages(c("tidyverse", "bayesrules"))`  in the Console.

```{r}
library(tidyverse)
library(bayesrules)

data("bikes")
```

## Question 1

Type ?bikes into the Console to view the data documentation. What is the description of the variables called `rides` and `temp_actual`?

### Response

`rides` refers to the number of bikeshare rides and `temp_actual` refers to raw
temperature measured in degrees Fahrenheit.

## Question 2

We want to explore if we can use the temperature to predict the number of daily bikeshare rides we will get. Produce a plot to visualize the relationship between `rides` and `temp_actual`. Make sure to provide axes labels instead of just using the default labels. (Hint: Look at slide 10 of lecture 4a.)

### Response

```{r}
ggplot(bikes, 
       aes(x = rides, y = temp_actual)) + 
  geom_point() +
  labs(
    x = "Number of Bikeshare Rides",
    y = "Temperature in Degrees Fahrenheit",
    title = "The Relationship Between Number of Bikeshare Rides and Temperature"
  )
```


## Question 3

Reproduce your plot from question 2, but now add a linear regression line to the plot. Does it appear to model your data well?

### Response

```{r}
ggplot(bikes, 
       aes(x = rides, y = temp_actual)) + 
  geom_point() +
  geom_smooth(method = lm,
              color = "purple") +
  labs(
    x = "Number of Bikeshare Rides",
    y = "Temperature in Degrees Fahrenheit",
    title = "The Relationship Between Number of Bikeshare Rides and Temperature"
  )
```
The regression line models the data fairly well. I can see that there is a positive
relationship between `temp_actual` and `rides` such that as `temp_actual` increases,
`rides` also increases.

## Question 4

Fit a linear model to regress `rides` on `temp_actual`, saving your model as `bike_model`. 
Note, I did not provide a code chunk for you to use for this question. You will have to click the "+C" button at the top of this document to add an R code chunk.

### Response

```{r}
bike_model <- lm(rides ~ temp_actual, data = bikes)

summary(bike_model)
```


## Question 5

Specify the fitted model in context.

### Response

$$\hat Y{Rides_i} = -2168.77 + 89.23(Temperature_i)$$

## Question 6

Interpret the estimate for the y-intercept in context. Does it have a meaningful interpretation in this context?

### Response

The expected number of `ride` when `temp_actual` is equal to 0 is -2168.77 `ride`s.
This does not have meaningful interpretation in context as there are no recorded
values in `temp_actual` equal to 0 and we would not expect a negative number of rides
as it is impossible.

## Question 7

Interpret the estimate for the slope in context.

### Response

The slope in this context is 89.23. For each unit increase in `temp_actual`, we expect
an increase in `ride` by 89.23.

## Question 8

Identify the 95% confidence interval for the slope and its corresponding margin of error.

### Response

```{r}
ci_bike <- confint(bike_model)["temp_actual", ]

# margin of error
bike_me <- (ci_bike[2] - ci_bike[1]) / 2 

ci_bike
bike_me
```


## Question 9

Improve your interpretation from question 7 here by adding the margin of error and confidence level into your interpretation.

### Response

A 1 degree increase in `temp_actual` is associated with an increase in bikeshare
`ride`s of 89.23 plus or minus 11.13949 rides with 95% confidence.

## Question 10

What daily number of rides would our model predict for a day where the temperature is 70 degrees Fahrenheit?

### Response

```{r}
temp_data <- data.frame(temp_actual = 70)

predict(bike_model, newdata = temp_data, interval = "confidence")
```


## Question 11

Identify the 95% interval for your prediction in question 10 and its corresponding margin of error.

### Response


## Question 12

Provide an interpretation of your prediction and interval from questions 10 and 11 in context, including your margin of error and confidence level into your interpretation.

### Response


## Question 13

What is the average daily number of rides would our model predict for days where the temperature is 70 degrees Fahrenheit?

### Response


## Question 14

Identify the 95% interval for your prediction in question 13 and its corresponding margin of error.

### Response


## Question 15

Provide an interpretation of your prediction and interval from questions 13 and 14 in context, including your margin of error and confidence level into your interpretation.

### Response


## Question 16

What daily number of rides would our model predict for a day where the temperature is 20 degrees Fahrenheit?

### Response


## Question 17

What is extrapolation and why is it dangerous?

### Response



# Homework Help

Have you done the homework by yourself, with a peer(s), or used tools like ChatGPT? 

- If you provided help to a peer(s) and/or got help from your peers(s) please explain briefly what this entailed. 
- If you used tools like ChatGPT, include the prompts you used and explain how the tool helped supported your learning.

## Response


