---
title: "DATA 308: Homework 3"
subtitle: "Simple linear regression"
author: "Dylan Wikel"
format: 
  html:
    echo: true
    message: false
    warning: false
    toc: true
    toc-depth: 4
    embed-resources: true
---

*Please change the author name to your own. Answer in complete sentences.*

# Bike share data

We have data on bike ridership among registered members of the Capital Bikeshare service in Washington, D.C. rentals by weather.

## Question 0

Begin by running the code chunk below to load the `tidyverse` package and the `bikes` data from the `bayesrules` package. You may need to first install the packages using `install.packages(c("tidyverse", "bayesrules"))`  in the Console.

```{r}
library(tidyverse)
library(bayesrules)

data("bikes")
```

## Question 1

Type ?bikes into the Console to view the data documentation. What is the description of the variables called `rides` and `temp_actual`?

### Response

[Replace this text and the brackets with your response.]

## Question 2

We want to explore if we can use the temperature to predict the number of daily bikeshare rides we will get. Produce a plot to visualize the relationship between `rides` and `temp_actual`. Make sure to provide axes labels instead of just using the default labels. (Hint: Look at slide 10 of lecture 4a.)

### Response

[Add your response to the R chunk below.]

```{r}

```


## Question 3

Reproduce your plot from question 2, but now add a linear regression line to the plot. Does it appear to model your data well?

### Response

```{r}

```


## Question 4

Fit a linear model to regress `rides` on `temp_actual`, saving your model as `bike_model`. 
Note, I did not provide a code chunk for you to use for this question. You will have to click the "+C" button at the top of this document to add an R code chunk.

### Response


## Question 5

Specify the fitted model in context.

### Response


## Question 6

Interpret the estimate for the y-intercept in context. Does it have a meaningful interpretation in this context?

### Response


## Question 7

Interpret the estimate for the slope in context.

### Response


## Question 8

Identify the 95% confidence interval for the slope and its corresponding margin of error.

### Response


## Question 9

Improve your interpretation from question 7 here by adding the margin of error and confidence level into your interpretation.

### Response


## Question 10

What daily number of rides would our model predict for a day where the temperature is 70 degrees Fahrenheit?

### Response


## Question 11

Identify the 95% interval for your prediction in question 10 and its corresponding margin of error.

### Response


## Question 12

Provide an interpretation of your prediction and interval from questions 10 and 11 in context, including your margin of error and confidence level into your interpretation.

### Response


## Question 13

What is the average daily number of rides would our model predict for days where the temperature is 70 degrees Fahrenheit?

### Response


## Question 14

Identify the 95% interval for your prediction in question 13 and its corresponding margin of error.

### Response


## Question 15

Provide an interpretation of your prediction and interval from questions 13 and 14 in context, including your margin of error and confidence level into your interpretation.

### Response


## Question 16

What daily number of rides would our model predict for a day where the temperature is 20 degrees Fahrenheit?

### Response


## Question 17

What is extrapolation and why is it dangerous?

### Response


# Homework Help

Have you done the homework by yourself, with a peer(s), or used tools like ChatGPT? 

- If you provided help to a peer(s) and/or got help from your peers(s) please explain briefly what this entailed. 
- If you used tools like ChatGPT, include the prompts you used and explain how the tool helped supported your learning.

## Response


