---
title: "DATA 308: Lab 6b"
subtitle: "Inference with SLR"
author: "Your name here"
format: 
  html:
    embed-resources: true
    toc: true
    toc-depth: 4
execute:
  message: false
  warning: false
---

```{r}
library(ggfortify)
library(openintro)
library(broom)
library(tidyverse)
```

# Instructions

For this activity we will:

1. Specify a simple linear regression model to investigate the relationship of interest.
2. Specify our hypotheses.
3. Fit the proposed model.
4. Assess suitability of our proposed model.
5. Report our statistical decision, conclusion in context, and estimate of the association, indicating any model sensitivity.


# Investigation

## Research question

The [High School and Beyond Survey](https://nces.ed.gov/surveys/hsb/) is a survey conducted on high school seniors by the National Center of Education Statistics.

> Among high school seniors represented by the High School and Beyond survey, is there evidence of a linear association between standardized math and science scores?

Let's consider standardized science scores to be our response variable.

## 1. Our model

State your proposed theoretical population model.

### Response

[Replace this text with your model. Recall you can use math notation like $Y_i$ and $\beta_0$.]

## 2. Hypotheses

State your hypotheses.

### Response

[Replace this text with your hypotheses. Recall you can use math notation like $H_0$ and $\beta_1$.]

## Data

We will use the `hsb2` dataset from the `openintro` R package to investigate our research question.
Start by entering `?hsb2` into the Console to bring up the help documentation, then run the code chunk below to glimpse your dataset.

```{r}
data("hsb2")

glimpse(hsb2)
```

## 3. Fitting your model

Fit your proposed model. 

### Response

```{r}

```

## Viewing estimated model

Use `tidy()` to display the estimated coefficients, their standard errors, test statistics, p-values, and 95% confidence intervals. 
We have used `summary()` and `confint()` in the past, this is a different option that shows us all the results we want together.

### Response

```{r}
# Replace NULL with the fitted model
tidy(
  NULL,
  conf.int = TRUE
)
```

## Estimate model

Write out the estimated regression equation.

### Response

[Replace this text with your estimated regression equation.]

## 4. Assessing model suitability

We will assess each model condition and then investigate whether the fitted model is sensitive to unusual observations.

### 1. Independence

Are you concerned that the independence condition is not satisfied?

AKA: Based on the available information in the help documentation, is it reasonable to treat the observations as independent? Explain what evidence supports your assessment and identify any limitations in the available study information.

#### Response

[Replace this text with your assessment of independence.]

### Diagnostic plots

Generate the four standard diagnostic plots.

#### Response

```{r}

```


### 2. Linearity

Are you concerned that the linearity condition is not satisfied?

#### Response

[Replace this text with your assessment of linearity. Refer to specific evidence from the plot.]

### 3. Constant variance

Are you concerned that the constant variance condition is not satisfied?

#### Response

[Replace this text with your assessment of constant variance. Refer to specific evidence from the plots.]

### 4. Normality

Are you concerned that the normality condition is not satisfied?

#### Response

[Replace this text with your assessment of normality. Refer to specific evidence from the plot or sample.]

### Sensitivity to unusual observations

Use the residuals-versus-leverage plot to identify observations that may have relatively high influence.
Are you concerned about any extreme observations? If so, use `slice()` to extract that observation. 

*We will do this together.*

#### Response

[Replace this text with your sensitivity analysis.]

## 5. Reporting your results

State your statistical decision with a significance level of 0.05.

### Response

[Replace this text with your statistical decision.]

## Conclusion in context

State your conclusion in context. Recall:

- One sentence should be your conclusion for the hypothesis test, with the p-value provided in parentheses. 
- The second sentence should be your estimate and 95% confidence interval interpreted in context.
- The third should mention if your results were especially sensitive to an extreme observation, and provide insight into that observation.

### Response

[Replace this text with your conclusion.]


# Final reflection

Why does this study allow us to investigate an association but not establish that higher math scores cause higher science scores? Identify at least two variables or characteristics that might help explain the observed association.

### Response

[Replace this text with your response.]

