---
title: "DATA 308: Lab 1b"
subtitle: "Working with data"
date: "2026-08-27"
author: "Dylan Wikel"
lang: en
format:
  pdf:
    pdf-standard: [a-2b, ua-2] # Configures PDF/A and PDF/UA-2 compliance
    pdf-engine: lualatex       # LuaLaTeX is highly recommended for tagging support
---

When working in a Quarto document I recommend:

- Start by rendering your document, so you know if there are any issues with the file.
- Render periodically as you work and inspect your rendered file, so you know your document and code are behaving as desired.

## Getting your data

0. In the code chunk below load in the `tidyverse` package.

```{r}
library(tidyverse)
```


1. In the code chunk below read in your data and save it into an object called `game_films`.

```{r}
game_films <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-06-09/game_films.csv')
```


2. Use the `glimpse()` function to inspect your data. How many rows and columns are there? Note, I did not add a code chunk for you. You will first need to click the green "+C" button at the top right of this document to add a code chunk.

There are `r ncol(game_films)` columns and `r nrow(game_films)` rows.
```{r}
glimpse(game_films)
```


## Explore your data

3. Reproduce a plot from the lecture slides.
```{r}
ggplot(game_films, aes(y = worldwide_box_office_currency)) +
  geom_bar()
```


4. Create a box plot using `geom_boxplot()` for a numerical variable of your choice.
```{r}
ggplot(game_films, aes(rotten_tomatoes)) +
  geom_boxplot()
```


5. Create a box plot of `worldwide_box_office` by `worldwide_box_office_currency`. Hint: you can do this by specifying `worldwide_box_office_currency` for your y-axis.
```{r}
ggplot(game_films, aes(x = worldwide_box_office, y = worldwide_box_office_currency, color = worldwide_box_office_currency)) +
  geom_boxplot()
```


6. Create a scatterplot for two numerical variables of your choosing, and add a smoothed curve.
```{r}
ggplot(game_films, aes(x = rotten_tomatoes, y = metacritic)) +
  geom_point() +
  geom_smooth(color = "purple") +
  coord_cartesian(xlim = c(0,100), ylim = c(0,100)) +
  labs(x = "Rotten Tomatoes Score",
       y = "Metacritic Score")
```


7. Calculate the minimum, maximum, 25\% quantile, and 75\% quantile of `rotten_tomatoes` scores.
```{r}
game_films |> 
  summarise(
    min_rt = min(rotten_tomatoes, na.rm = TRUE),
    max_rt = max(rotten_tomatoes, na.rm = TRUE),
    q1_rt = quantile(rotten_tomatoes, 0.25, na.rm = TRUE),
    q3_rt = quantile(rotten_tomatoes, 0.75, na.rm = TRUE)
  )
```


## Version control

I do recommend using GitHub for this class, but I will not require for homework assignments, just the final project.
I recommend you practice by using a single GitHub repository for your labs and homework assignments for this class.

Here are [instructions I created for installing and configuring GitHub and RStudio]( https://csuci-data-200-f26.github.io/lecture-materials/week-00/software-setup). (Skip step 4)

