---
title: "DATA 208: Lab 1a"
subtitle: "Familiarizing yourself with a Quarto document"
date: "2026-08-25"
author: "Dylan Wikel"
lang: en
format: 
  html:
    echo: false
    message: false
    warning: false
    toc: true
    toc-depth: 4
    embed-resources: true
---

```{r}
library(tidyverse)
```

Start off this lab by clicking the "Render" (the blue arrow) at the top. This will produce an html report, where you can view the plots and questions. The .qmd file is a Quarto document, this document is where you will make changes, render, and then see those changes reflected in the html report it procudes.


In this lab we will be exploring California unemployment rates.
This data is available on the [CA Open Data Portal](https://data.ca.gov/dataset/unemployment-rate-by-age-groups).

We will begin by reading in this data and saving it into an **object** called `unemployment`.

```{r}
unemployment <- read_csv("http://csuci-data308-fa26.github.io/course-materials/week-01/data/unemployment_rate_by_age_groups.csv")
```

We can view what is in the `employment` object by printing it.

```{r}
unemployment
```

You can skip over the following code chunk, I needed to do some data cleaning and wrangling to get it in a good format for plotting.

```{r}
unemployment_new <- unemployment |>
  mutate(new_date = as_date(Date, format = "%m/%d/%Y")) |> 
  pivot_longer(
    cols = starts_with("Age "),
    names_to = "age_group",
    names_prefix = "Age ",
    values_to = "unemployment_rate"
  )
```


## Unemployment over time

```{r}
unemployment_new |> 
  filter(age_group == "25-34") |> 
  ggplot(aes(x = new_date, y = unemployment_rate)) +
  geom_point() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    x = "Date",
    y = "Unemployment rate \n for individuals ages 25-34"
  )
```

## Question 1

If you were to describe these trends to someone what would you say?

### Response

Unemployment rates for individuals in the 25-34 age range were fairly low
in the year 2008, increased and peaked around 2012, and dropped considerably
near 2020, with a marked rise and fall between 2020 and present time.

## Question 2

What is a "typical" unemployment rate? What would be an unusual rate?

### Response

A typical unemployment rate would be roughly 5% and an unusual unemployment
rate would be 10-12%.

## Unemployment trends for each age group

```{r}
ggplot(
  unemployment_new, 
  aes(x = new_date, y = unemployment_rate, color = age_group, linetype = age_group)
) +
  geom_line() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    x = "Date",
    y = "Unemployment rate",
    color = "Age group",
    linetype = "Age group"
  )
```

## Question 3

Given this data, what would you predict the average unemployment rate of 2027 to be for people aged 25-34? Why?

### Response

I would expect the average unemployment rate for people aged 25-34 in 2027 to 
be around 5% because there was less variability or fluctuation in the couple of
years prior. Because it was hovering around 5% already, I'd expect little change.

## Question 4

Given this data, what would you predict the average unemployment rate of 2035 to be for people aged 55-64? Why?

### Response

I think that it would be unwise to predict an unemployment rate 10 years beyond
our dataset based on a visual alone. Based on previous data, drastic increases
and decreases in unemployment rates for all groups can occur in short timespans.
But, I would predict that this age group would see lower overall increases and
decreases when compared to other groups as the higher age groups unemployment
rates appear more stable than those in lower age groups.


## Question 5

Which age group(s) had the highest unemployment rate in general?

### Response

Age groups 16-19.

## Question 6

Which age group(s) had the lowest unemployment rate in general?

### Response

People in the groups aged 45-54, 55-64, and 65+ have the lowest unemployment 
rates.

## Question 7

Would you say there is a meaningful difference in unemployment rates between 55-64 year olds and 20-24 year olds? Why?

### Response

Yes, as it appears that the unemployment rate for 20-24 year olds is roughly
1.5x-2.0x the rate of 55-64 year olds across the graph.

## Question 8

Would you say there is a meaningful difference in unemployment rates between 55-64 year olds and 35-34 year olds? Why?

### Response

No, it appears to only differ between 1-3% between these groups across the graph.


When you are done, click "Render" (the blue arrow) at the top. Submit the rendered html report to CI Learn.
