---
title: "DATA 308: Homework 5"
subtitle: "Multiple linear regression"
author: "Dylan Wikel
format: pdf
knitr:
  opts_chunk:
    message: false
    warning: false
    echo: true
---

```{r}
library(ISLR2)
library(janitor)
library(tidyverse)

data("Carseats")
```


## Question 1

This question should be answered using the `car_seats` data set. `car_seats` is a cleaned version of the data I made, to view the data documentation you must search `?Carseats`

```{r}
car_seats <- Carseats |> 
  mutate(
    ShelveLoc = factor(ShelveLoc,levels = c("Bad", "Medium", "Good")),
    US = factor(US, levels = c(FALSE, TRUE))
  ) |> 
  clean_names()
```

Run the code below to view 2-D scatter plots of sales plotted against selected predictors.
```{r}
car_seats |> 
  select(sales, price, urban, shelve_loc, age) |> 
  pairs()
```


### Question 1a

Fit a multiple regression model to predict `sales` using `price`, `urban`, `shelve_loc` and `age`.

#### Response


```{r}
car_seat_mlr <- lm(sales ~ price + urban + shelve_loc + age, car_seats)

car_seat_mlr
```

### Question 1b 

Write out the theoretical population model, being careful to handle the qualitative variables properly.

#### Response



### Question 1c 

Write out your fitted model, being careful to handle the qualitative variables properly.

#### Response




### Question 1d

Provide an interpretation of each coefficient in the model. Be careful—some of the variables in the model are qualitative!

#### Response



### Question 1e

Using the original full model, obtain 95 % confidence intervals for each of the coefficients (i.e., slopes).

#### Response




### Question 1f

If we wanted confidence intervals with a confidence level of 99%, would they be narrower or wider than the 95% confidence intervals?

#### Response




### Question 1g

Using the original full model, compute a 95% prediction interval for the number of sales when a car seat price is $100, its sold in an urban location, has a good shelving location, and the average age of the local population is 30.

#### Response




### Question 1h

We would expect price to be very related to the number of sales made. Conduct a hypothesis test to assess if any of the remaining explanatory variables are linearly related to number of car seats sold, when price is in the model.

#### Response




### Question 1i

In which of the models (a) or (subsetted model from part h) is the standard error for the price slope larger? Why do you think that is?

#### Response




## Question 2

In this problem we will investigate the t-statistic for the null hypothesis $H_0 : \beta = 0$ in simple linear regression without an intercept. To begin, run this code to simulate an explanatory x and a response y as follows.
```{r}
set.seed(1) # Setting a random seed makes it reproducible. It is useful when you are going to randomly generate numbers

x <- rnorm(100) # Generated 100 standard normal random variables
y <- 2 * x + rnorm(100) # Calculates Y with more added randomness

simulated_data <- data.frame(x = x, y = y)
```

### Question 2a 

Perform a simple linear regression of $y$ onto $x$ from `simulated_data`, without an intercept. Report: 

- the coefficient estimate $\hat{\beta}_1$, 
- the standard error of this coefficient estimate, and 
- the t-statistic and p-value associated with the null hypothesis $H_0 : \beta_1 = 0$. 

(You can perform regression without an intercept using the command `lm(y ∼ 0 + x, data = simulated_data)`.)

#### Response



### Question 2b

Now perform a simple linear regression of $x$ onto $y$ without an intercept, and report:

- coefficient estimate $\hat{\beta}_1$, 
- its standard error, and 
- the corresponding t-statistic and p-values associated with the null hypothesis $H_0 : \beta_1 = 0$. 

#### Response



### Question 2c

What is the relationship between the results obtained in (2a) and (2b)? Specifically, what is the same and what is different, if anything?

#### Response


